---
title: "RunkeeperStats"
author: "CTV"
date: "November 20, 2015"
output: html_document
runtime: shiny
---

Lets explore my Runkeeper data...


```{r, echo=FALSE}

# imports packages and functions I need
source("~/DataScience/RFirst.R")

library(shiny)


cardio=read.csv('~/DataScience/DataSets/runkeeper/cardioActivities.csv',stringsAsFactors=FALSE,na.strings="")

names(cardio)=qw("dt type routename distance duration pace speed calories climb hr notes gpx")
cardio$dt=parse_date_time(cardio$dt,"ymd_hms")
cardio=mutate(cardio,year=year(cardio$dt),paceSeconds=period_to_seconds(ms(pace)))

radioButtons("extype",label="Choose Type of Exercise",choices=c('Running','Cycling','Downhill Skiing'))

exmat=reactive({
  filter(cardio,type==input$extype)
  })



```

Input type is `r renderText({input$extype})`
There are `r renderText({nrow(exmat())})` measurements from `r renderText({input$extype})`
Mintime = `r renderText({min(exmat()$paceSeconds,na.rm=T)})`

``` {r echo=FALSE}
# 
# renderPlot ({
#  qplot(distance,pace,data=exmat(),geom="point")
# })

renderPlot ({
  maxtime=max(exmat()$paceSeconds,na.rm=T)
  mintime=min(exmat()$paceSeconds,na.rm=T)
  g=ggplot(exmat(),aes(x=distance,y=paceSeconds,color=year))
  g + geom_point() +
    scale_y_continuous(breaks=c(seq(0,maxtime,120)),
                       labels=paste0(as.character(seq(0,maxtime,120)/60),":00"))
    
})

