---
title: "Stat416 Homework 5"
author: "Yihui Xie"
date: "04/09/2014"
output:
  html_document: default
  pdf_document:
    toc: yes
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(tidy = TRUE)
```

In this homework, we were asked to find out the genes that should be identified as differentially expressed. Here we go.

First we read the P-values into R:

```{r read-pvalues, echo=TRUE}
# set the alpha level
a = 0.05
# read the P-values
p = scan('01-hwk5_q1.txt')
p  # print them
par(mar = c(4, 4, .1, .1))
barplot(p, names.arg = seq_along(p))
abline(h = a, col = 'red')
```

We need to adjust these `r length(p)` P-values using these methods:

- Bonferroni's method (threshhold $c = \alpha/m$)
- Holm's method (largest $i$ s.t. $p_{(i)} \leq \alpha/(m - i + 1)$)
- Benjamini and Hochberg's method

## Hard-working students

To understand our methods completely, we have to write every piece of code by hand. For example, we write the Bonferroni's method below, and pick out the genes:

```{r}
#' @param pv a vector of P-values
#' @param alpha the alpha level
#' @return the indices of the genes
p_bonferroni = function(pv, alpha = 0.05) {
  m = length(pv)
  c = alpha/m
  which(pv <= c)
}
p_bonferroni(p)
p_holm = function(...) {
  ...
}
p_BH = function(...) {
  ...
}
```

Now we have finished our homework, and we are confident that we understand how each method works in practice.

## Lazy (but smart) students

Some students quickly realized the `p.adjust()` function in base R. Five minutes later, they finished the homework and went for beer. Yeah!

```{r}
(p1 = p.adjust(p, method = 'bonferroni'))
(p2 = p.adjust(p, method = 'holm'))
(p3 = p.adjust(p, method = 'BH'))
```

## Final results

```{r include=FALSE}
#' @param i the indices of genes
gene_list = function(i) {
  if (is.logical(i)) {
    i = which(i)
  }
  n = length(i)
  text = if (n <= 1) {
    i
  } else if (n == 2) {
    paste(i[1], i[2], sep = ' and ')
  } else {
    paste(i, rep(c(', ', ', and ', ''), c(n - 2, 1, 1)), sep = '', collapse = '')
  }
  paste('the', ifelse(n <= 1, 'gene', 'genes'), text)
}
# test this little function
gene_list(1)
gene_list(c(1, 3))
gene_list(1:10)
gene_list(c(TRUE, FALSE, FALSE, TRUE, TRUE))
```

We identified `r gene_list(p1 <= a)` using Bonferroni's method, `r gene_list(p2 <= a)` using Holm's method, and `r gene_list(p3 <= a)` using BH's method.
