---
title: "ggvis in an interactive document"
output: html_document
runtime: shiny
---

```{r echo=FALSE, message=FALSE}
# We used echo = FALSE and message = FALSE to suppress output of this code block

# Load some needed packages
library(knitr)
library(ggvis)
library(shiny)
```

A static plot:

```{r, message = FALSE, fig.width = 4, fig.height = 3}
cocaine %>%
  ggvis(x = ~weight, y = ~price) %>%
  layer_points(size = ~potency, opacity := 0.2)
```


An interactive plot:

```{r, message = FALSE, fig.width = 6, fig.height = 4}
mtcars %>%
  ggvis(x = ~wt, y = ~mpg) %>%
  layer_points() %>%
  layer_smooths(span = input_slider(min = 0.2, max = 2, value = 0.5, step = 0.1))
```


## Plot with separate controls

It's also possible to create a plot with controls separately. It's a little more complicated, but one advantage is that the inputs can be re-used for other purposes as well.

```{r, message = FALSE, fig.width = 6, fig.height = 4}
# Note: we need to wrap input$bw_slider in reactive() for ggvis to
# properly understand it.
cocaine %>%
  ggvis(x = ~potency) %>%
  layer_histograms(width = reactive(input$bw_slider))
```

We'll add the slider separately:

```{r}
sliderInput("bw_slider", label = "bin width", min = 1, max = 20, value = 11)
```


And we can also have a table that updates dynamically in response to the slider:

```{r}
renderTable({
  cocaine %>% compute_bin(x_var = ~potency, width = input$bw_slider)
})
```

Note that in most cases when you use an `input$xx` value in an interactive document, it must be wrapped in `reactive()` or a `renderXxx()` function. These include `renderText()`, `renderPrint()`, `renderTable()`, and `renderDataTable()`.
