---
title: "ShinyWeight"
author: "CTV"
date: "October 9, 2015"
output: html_document
runtime: shiny
---

I have measured my weight every day for the past few years using a [Withings Wifi scale](http://www.withings.com/us/en/products/smart-body-analyzer).  Here is a visualization of that.

The date range and the smoothing parameter can be adjusted via shiny widgets. 

```{r, echo=FALSE}
library(dplyr)
library(ggplot2)
library(lubridate)
source("RFirst.R")

datafile="LatestWeight.csv"
weight=read.csv(datafile,header=T)
names(weight)=qw("ts weight fat lean comments")
weight$ts = parse_date_time(weight$ts,"%Y-%m-%d %H:%M %p")

dateInput("startdate",label="Start Date",value=min(weight$ts))

dateInput("enddate",label="End Date",value=max(weight$ts))

sliderInput("numspan",label="Span of Loess Smooth",min=0.05,max=0.5,step=0.05,value=0.25)

wtmat=reactive({
  filter(weight,weight$ts>=ymd(input$startdate) & weight$ts<ymd(input$enddate))
  })



```


There are **`r renderText({nrow(wtmat())})`** measurements between **`r renderText({as.character(input$startdate)})`** and **`r renderText({as.character(input$enddate)})`** with an average weight of  **`r renderText({round(mean(wtmat()$weight,na.rm=TRUE),2)})` **

``` {r echo=FALSE}

# this works!! 
#renderPlot ({
#  qplot(ts,weight,data=wtmat(),geom="line")
#})

renderPlot ({
  p=ggplot(wtmat(),aes(ts,weight),main="Plot") + 
    geom_point(alpha=0.8) + 
    stat_smooth(method="loess",size=2,se=FALSE,span=input$numspan) 
  p
})




